Human-level control through deep reinforcement learning

### 2017-12-23 article/article.tex
[Article] Nothing of much interest

  Reinforcement learning is a subarea of machine learning inspired by neuroscience, where learners have to select actions with
  regards to the environement state and receive a reward accordingly. Each agent's objective is to maximize its cumulative reward across its whole lifetime,
  subdivided into episodes. In the traditional framework of reinforcement learning and more specifically in Q-learning,
  researchers usually deal with a small discrete space to represent the values of Q. This is no longer sufficient if one desires to describe the environment state
  as an image of raw pixels. In consequence, we introduce deep Q-learning methods, which have been found to be really effective in mapping raw pixels
  to abstract high-level features. In deep Q-learning, the estimation of Q-values for a given action are produced using deep neural networks,
  which consist of many neural layers stacked on top of each other. 
  These techniques have revealed themselves to be able to beat human experts at playing Atari games 
  by learning only from visual features. Despite the current progress, learning to take complex decisions on the basis of high-dimensional visual data remains on
  ongoing challenge.

@@

Since we are handling visual features, we used screen frames as environment state representations. Each frame is a (210 x 160) color image sampled at
a frequency of 60 Hz.

@@

>>>>

  Reinforcement learning is a subarea of machine learning inspired by neuroscience, where learners have to select actions with
  regards to the environement state and receive a reward accordingly. Each agent's objective is to maximize its cumulative reward across its whole lifetime,
  subdivided into episodes. In the traditional framework of reinforcement learning and more specifically in Q-learning,
  researchers usually deal with a small discrete space to represent the values of Q. This is no longer sufficient if one desires to describe the environment state
  as an image of raw pixels. In consequence, we introduce deep Q-learning methods, which have been found to be really effective in mapping raw pixels
  to abstract high-level features. In deep Q-learning, the estimation of Q-values for a given action are produced using deep neural networks,
  which consist of many neural layers stacked on top of each other. 
  These techniques have revealed themselves to be able to beat human experts at playing Atari games 
  by learning only from visual features. Despite the current progress, learning to take complex decisions on the basis of high-dimensional visual data remains on
  ongoing challenge. In particular, because of the instability of neural networks, we also explored state-of-the-art dueling architectures to enhance performance
  by separating the high-level representation of states and action values (rewards).

@@

Since we are handling visual features, we used screen frames as environment state representations. Each frame is a (210 x 160) color image sampled at
a frequency of 60 Hz. We denote the environment state at current step $t$ by $s_t$. The agent gathers experience by incorporating new experience samples
to its history. An experience is a tuple $e_t = (s_t, a_t, r_t, s_{t+1})$ appended to the experience history immediately after being generated.
To prevent the agent from forgetting the history and increase the bias towards most recent experience samples, we have recourse on the experience
replay algorithm. One can straightforwardly implement it as a uniform sampling algorithm that returns random experience samples at each step.
We compared this technique to a more efficient approach called prioritized experience replay \citep{DBLP:journals/corr/SchaulQAS15}.

@@

It has been shown that DQN has an ability to learn by acquiring experience generated from policies other than its own.
